Coherent optical association of a single molecule

### 2020-10-29 paper.tex
White space, regenerate PDF
Reply to Jon
WIP: address Jons comments

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\eff}{ef\! f}
\newcommand{\fxnote}[1]{{\textbf{[#1]}}}

@@

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. The Raman scheme uses a deeply bound electronic excited intermediate state to achieve a large transition dipole moment while reducing the photon scattering. 
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69\%$.
  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power. We can state the tweezer power for where we measure it, but the transmission through the objective, etc. I believe is only estimated.})
  with more than $60\%$ of the molecule created in the motional ground state.
  This technique does not rely on narrow excited state lines or Feshbach resonances and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques that have been developed for atoms. Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy. A two-step approach has been demonstrated to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance. The only exceptions are Sr$_2,$ where narrow linewidth ($\sim 20 ~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly bound molecules with a couple MHz binding energy exists~\cite{He331}. With these requirements, dimers between alkali atoms and non-magnetic atoms, or molecules involving atoms without narrow intercombination lines remain difficult to associate. 
% These requirements limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A. The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state. The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state. A vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation. To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible. This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control. 
% and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
% (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))

@@

% The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance \todo{cite our FB result}. However, this requires a suitable Feshbach resonance, which limits the generality of this technique. An alternative approach uses a weakly bound ground electronic molecular state as the intermediate state (I'm wondering how we can distinguish this weakly bound molecular state from the weakly-bound Feshbach molecule state, we can maybe specify typcial binding energies? "most weakly bound state of the low field ground state electronic potential" maybe?), populated by an optical Raman transition, schematically shown in figure \todo{}. In this scheme, a pair of Raman beams is used to drive the unbound, but confined, atoms to a bound molecular state via an excited molecular state. This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules. Such a transfer using an optical transition has been observed in previous experiments \todo{cite}. However, they either require the use of a narrow optical transition which limits the generality or were driving the transition incoherently due to scattering.

% the requirement of a suitable FB resonance limits its generality. \todo{e.g. non-magnetic atoms?}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (A) Schematics of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (B) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (C) Enhancement of short range wavefunction.
    The large scattering length for the $Na(2,2),Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\mathrm{\AA}$) is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

@@

% The optical transfer scheme we use is shown in figure \todo{}. To drive the atoms from
% We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state. In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state. \todo{move selection of intermediate state to intro?}. For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency. Therefore, in our experiment, we selected the v'=0 state as the intermediate state for our Raman transition.

@@

% The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state. While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
% Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser frequencies with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}.
Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the target molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally. Thus, the scattering is given by $ \Gamma_s=\Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.

Early experiments used weakly-bound excited states as the intermediate state in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}. However, for a complete picture, the many excited vibrational states in a molecular potential as well as the excited atomic continuum need to be considered. The total scattering rate and Raman Rabi rate become a sum of the scattering rates and Raman Rabi rates over all possible intermediate states. With these considerations, using a weakly-bound excited state as the intermeidate state suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent, resulting in molecule loss. This scattering is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.
%With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states. Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state. The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum. (See SM)

% For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
% Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
% (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)

To find the optimal intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011} and the continuum~\cite{Liu2017}. The excited atomic continuum is particularly important for the target molecular state. The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum (See SM).
This calculation shows that the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency (Fig.~\ref{f-theory}B, full result in SM)
As a result, we choose %a deeply bound molecular excited state
the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state to drive the Raman transition. %(mention the trend, also v'=12 will work as similarly as v'=0)

% higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states. As a result, we use a deeply bound molecular excited state to drive the Raman transition.

@@

In addition to the intermediate state, choosing an initial and a final state for a large $ \Omega_a/\Omega_m $ ratio would allow large Raman Rabi coupling at a given detuning. Furthermore, a larger ratio also relaxes the intensity stability requirement, because this is also the ratio between the Raman Rabi coupling and the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2, with both beams at equal power, to account for the Stark shift caused by both beams.}.

@@

Due to the small size of the intermediate state wavefunction, the coupling $\Omega_a$ is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. To increase the amplitude within the molecular potential, one can increase the external confinement of atom pairs. Using a harmonic oscillator approximation, the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $, where $ \omega_{\text{trap}} $ is the trap frequency. Alternatively, one can choose an atomic pair state with a large scattering length (positive or negative).
For these states, the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C). %The increase in the coupling is proportional to (quote/cite Olive's equation?).
For our system of Na and Cs atoms, we choose  a spin state combination $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=3,m_F=3}_{\text{Cs}} $that has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0$~\cite{Hood2019}. We note that other stable spin combinations give smaller scattering lengths ($<~50~a_0$).

>>>>

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\eff}{ef\! f}
\newcommand{\Na}{\mathrm{Na}}
\newcommand{\Cs}{\mathrm{Cs}}
\newcommand{\fxnote}[1]{{\textbf{[#1]}}}

@@

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69\%$.
  The molecule has a binding energy of $770.20052(2) \mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power. We can state the tweezer power for where we measure it, but the transmission through the objective, etc. I believe is only estimated. (YYC: This is why the original number quoted was zero field. The current number is still for zero tweezer power)})
  with more than $60\%$ of the molecule created in the motional ground state.
  This technique does not rely on narrow excited state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques that have been developed for atoms. Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy. A two-step approach has been demonstrated to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance. The only exceptions are Sr$_2,$ where narrow linewidth ($\sim 20 ~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}. With these requirements, dimers between alkali atoms and non-magnetic atoms, or molecules involving atoms without narrow intercombination lines remain difficult to associate.
% These requirements limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly-bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a. The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state. The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state. A vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation. To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible. This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control.
% and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
% (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))

@@

% The traditional choice for such an intermediate state is a weakly-bound Feshbach molecule, which can be coherently produced by ramping a magnetic field across the Feshbach resonance. However, this requires a suitable Feshbach resonance, which limits the generality of this technique. An alternative approach uses a weakly-bound ground electronic molecular state as the intermediate state (I'm wondering how we can distinguish this weakly-bound molecular state from the weakly-bound Feshbach molecule state, we can maybe specify typcial binding energies? "most weakly-bound state of the low field ground state electronic potential" maybe?), populated by an optical Raman transition, schematically shown in figure. In this scheme, a pair of Raman beams is used to drive the unbound, but confined, atoms to a bound molecular state via an excited molecular state. This approach minimizes the reliance on system specific properties and can therefore be more generally applied to creating other molecules. Such a transfer using an optical transition has been observed in previous experiments. However, they either require the use of a narrow optical transition which limits the generality or were driving the transition incoherently due to scattering.

% the requirement of a suitable FB resonance limits its generality.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematics of the optical transition from an atom pair to a weakly-bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (b) Comparison between using a weakly-bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (c) Enhancement of short range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\mathrm{\AA}$) is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

@@

% The optical transfer scheme we use is shown in figure. To drive the atoms from
% We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state. In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state as our final state. For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency. Therefore, in our experiment, we selected the v'=0 state as the intermediate state for our Raman transition.

@@

% The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state. While pioneering experiments used weakly-bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
% Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser frequencies with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}.
Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the target molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally. Thus, the scattering is given by $ \Gamma_s=\Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.

Early experiments used weakly-bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, for a complete picture, the many excited vibrational states in a molecular potential
as well as the excited atomic continuum need to be considered.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly-bound excited state as the intermeidate state
suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
resulting in molecule loss \todo{be more clear with "molecule loss". I think you mean:
  resulting in large incoherence and loss to other molecular states.}.
This scattering is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.
% With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states. Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state. The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum. (See SM)

% For a weakly-bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
% Furthermore, due to similarity in wavefunction size, the weakly-bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
% (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency
and scattering rate at different detunings from the atomic threshold
taking into account of all states of
the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
and the continuum~\cite{Liu2017}.
The excited atomic continuum is particularly important for the target molecular state.
The sum of the squares of the wavefunction overlap
between the target weakly-bound molecular state
and all the excited molecular intermediate states considered
\todo{all vibrational states} is only about $0.02$,
suggesting that there is significant matrix element
between the target molecular state and the excited atomic continuum (See SM).
This calculation shows that the ratio of the Raman Rabi rate to scattering rate
can be made larger for more deeply bound states compared to weakly-bound states
at a cost of a smaller Raman Rabi frequency
(Fig.~\ref{f-theory}b, full result in SM \todo{proper cite})
As a result, we choose the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state
to drive the Raman transition. % (mention the trend, also v'=12 will work as similarly as v'=0)

% higher Raman Rabi frequency at the same detuning, using a weakly-bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states. As a result, we use a deeply bound molecular excited state to drive the Raman transition.

@@

In addition to the intermediate state,
choosing an initial and a final state for a large $ \Omega_a/\Omega_m $ ratio
maximizes Raman Rabi coupling at a given detuning.
Furthermore, a larger ratio also relaxes the intensity stability requirement,
because this is also the ratio between the Raman Rabi coupling
and the AC Stark shift of the molecular state, $\Omega_m^2 / 2\Delta$
\footnote{There is an additional factor of 2, with both beams at equal power,
  to account for the Stark shift caused by both beams.}.

@@

Due to the small size of the intermediate state wavefunction as compared to the trapped atoms,
the coupling $\Omega_a$ is approximately proportional to
the value of the relative atomic wavefunction at short distance
within the molecular potential.
To increase the amplitude within the molecular potential,
one can increase the external confinement of atom pairs.
Using a harmonic oscillator approximation,
the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $,
where $ \omega_{\text{trap}} $ is the trap frequency.
Alternatively, one can choose an atomic pair state with a large scattering length
(positive or negative).
For these states, the phase shift in the relative wavefunction
between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}c).
% The increase in the coupling is proportional to (quote/cite Olive's equation?).
For our system of Na and Cs atoms,
we choose a spin state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
$ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.
All other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\Cs}} = \ket{F=4,m_F=4}_{\Cs}, \ket{\downarrow_{\Cs}} = \ket{F=3,m_F=3}_{\Cs}, \ket{\uparrow_{\Na}} = \ket{F=2,m_F=2}_{\Na}, $ and $ \ket{\downarrow_{\Na}} = \ket{F=1,m_F=1}_{\Na}$. Among the stable spin combinations, $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\Na} \downarrow_{\Cs}} $ combination has a large and negative scattering length of $ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
For the target molecular state, we perform coupled-channel calculations
to identify the Rabi frequencies $\Omega_m$ to different weakly-bound spin states.
\text{red}{A target spin state is ideally similar to the initial spin state
  in order to minimize sensitivity to the B-field.
  We find a target spin state predominantly in the initial spin state
  that also has the advantage of having a reduced sensitivity
  to laser intensity noise because of a larger $\Omega_a/\Omega_b$ as compared to other states.
  This reduces the intensity stability requirement to $5\%$
  instead of $0.3\%$ which is typical for other states.}
In addition to the increased atomic coupling, $ \Omega_a $,
coupled channel calculations show that the target molecular state
